`tidyfun`

### 2019-06-09 teaching.Rmd
add webinar info
update directory name ("Downloads" -> "resources")
typo fix, general update of infrastructure

Fall 2018: [Data Science I](http://p8105.com)

@@

Fall 2017: Data Science I
Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  
Spring 2015: Linear Regression Models  
Summer 2015: Applied Regression II  
Spring 2014: Linear Regression Models  
Spring 2014: Categorical Data Analysis  
Spring 2013: Linear Regression Models  
Spring 2013: Categorical Data Analysis

@@

>>>>

Fall 2019: [Data Science I](http://p8105.com)

@@

Fall 2018: [Data Science I](http://p8105.com)  
Fall 2017: [Data Science I](http://p8105.com)  
Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  
Spring 2015: Linear Regression Models  
Summer 2015: Applied Regression II  
Spring 2014: Linear Regression Models  
Spring 2014: Categorical Data Analysis  
Spring 2013: Linear Regression Models  
Spring 2013: Categorical Data Analysis

@@

## Other materials

2018: Webinar: ["Data Science and Predictive Models in Public Health"]() and accompanying [reproducible lasso example](resources/lasso_example.zip) (webinar requires registration of free account)
